The Structure of Human Language Reflects Limitations of Working Memory

### 2019-05-03 paper-short.tex
some changes

\begin{abstract}
  %  the Nature template:
  % 1-2 sentences basic introduction, for anyone
  Each of the roughly 6000 natural languages currently spoken in the world embodies a different system for encoding thoughts into linear strings of words.
  By characterizing the commonalities and differences among these systems we can gain insight into the cognitive machinery that underpins this fundamental aspect of human intelligence. 
  % 2-3 sentences detailed background, for scientists in related disciplines (linguistics, cogsci, computer science, info theory)
  In linguistics and cognitive science, there have been two \jd{unfinished sentence}

  % 1 sentence general problem
  % 1 sentence here we show
  Here we show that the order of words across human languages is structured to enable efficient transfer of information under the constraint that language must be comprehended and produced by agents with limited short-term memory capacities.
  We directly show that languages are optimized to minimize memory usage by calculating lower bounds on the amount of memory resources required for language comprehension in TODO \jd{random TODO} real languages and in random baseline languages, finding that the real languages require less memory.
  % 2-3 sentences how main result adds to knowledge
  Using concepts from information theory, we prove a theorem showing that any efficient communication system operating under memory constraints will exhibit a property called information locality: symbols which predict each other should be produced close to each other in time.
  We show that information locality subsumes several principles of word order previously proposed in the linguistics and cognitive science literature, and explains a number of the previously-documented universal patterns in word order across languages.    
	% TODO i'm wondering whether we should first mention the big result, and then say, well it also subsumes previously proposed constraints.
  % 1-2 sentences general context

  % 2-3 sentences broader perspective
  Our results suggest a view of natural language as a maximally efficient code for communication, subject to the particular information-processing constraints of the human mind. 
\end{abstract}

>>>>

\begin{abstract}
  %  the Nature template:
  % 1-2 sentences basic introduction, for anyone
  Each of the roughly 6000 natural languages currently spoken in the world embodies a different system for encoding thoughts into linear strings of words.
  By characterizing the commonalities and differences among these systems we can gain insight into the cognitive machinery that underpins this fundamental aspect of human intelligence. 
  % 2-3 sentences detailed background, for scientists in related disciplines (linguistics, cogsci, computer science, info theory)
  In linguistics and cognitive science, there has been a persistent suggestion that the properties of human languages can be explained in terms of maximizing communicative efficiency under the cognitive constraints involved in language production and comprehension \citep{gibson2019efficiency,florian,hawkins,piantadosi2011word,zipf1949}.

  % 1 sentence general problem
  % 1 sentence here we show
  Here we give evidence for this view by showing that human languages structure information in time so as to enable efficient communication under the constraint that language must be comprehended and produced by agents with limited short-term memory resources.
  We directly show that languages minimize memory usage by calculating information-theoretic bounds on the amount of memory resources required for language comprehension in 54 real languages and in random baseline languages, finding that the real languages require less memory.
  % 2-3 sentences how main result adds to knowledge
  To explain how languages achieve this result, we prove a theorem showing that any efficient communication system operating under memory constraints will exhibit a property called information locality: symbols which predict each other should be produced close to each other in time.
  We show that information locality subsumes several principles of word order previously proposed in the linguistics and cognitive science literature, and explains a number of the previously-documented universal patterns in word order across languages.
	% TODO i'm wondering whether we should first mention the big result, and then say, well it also subsumes previously proposed constraints.
  % 1-2 sentences general context

  % 2-3 sentences broader perspective
  Our results suggest that human languages can be modeled as solutions to the problem of maximally efficient communication subject to the particular information-processing constraints of the human mind. 
\end{abstract}
